Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-29 colt-21/cvx-flats.tex
Adding comments on proof of Lemma 11

\begin{lemma}
	  \label{lem:convex-flats-inf-dim}
	Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
	When $\Y = \reals$, we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.%
        \footnote{\raf{This assumption is for technical convenience...}}
	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
\end{lemma}
\begin{proof}
  As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
  We proceed in two cases, depending on $|\Y|$.

@@

  \emph{$\Y=\reals$: }
  Any $L \in \Lcvx_d$ satisfies the assumptions of~\cite{ioffe1969minimization}, so we may interchange subdifferentiation and expectation.
  Specifically, letting $\V_{u,p} = \{V:\Y\to\reals^d \mid V \text{ measurable}, V(y) \in \partial L(u,y) \text{ $p$-a.s.}\}$, we have
  $\partial \E_p L(u,Y) = \{\int V(y)dp(y) \mid V\in\V_{u,p}\}$.
  As $\vec 0 \in \partial \E_p L(u,Y)$, in particular, there is some $V_{u,p} \in \V_{u,p}$ such that $\E_p V_{u,p} = 0$.
  For any $q\in\P$, as by assumption $q$ is supported on the same set as $p$, we have $V_{u,p}(y)\in\partial L(u,y)$ $q$-a.s., so that $V_{u,p}\in\V_{u,q}$\raft{I'm a bit too tired to see exactly how this follows, but it seems intuitively obvious. I'm okay to punt on it for the submission, but if someone has time to check, that would be great!}.
  Thus, $\E_q V_{u,p} = 0$ implies $0\in\partial\E_q L(u,Y)$ by the above.
  \raft{For posterity, the bug: we want to conclude $\E_q V_{u,p} = 0 \implies q \in \Gamma_u$.  But the ``a.s.\ in $p$'' means we may not have $0 \in \partial \E_q L(u,Y)$, since maybe $V_{u,p}(y)$ is not in $\partial L(u,y)$ a.s.\ in $q$...}

>>>>

\begin{lemma}
	  \label{lem:convex-flats-inf-dim}
	Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
	When $\Y = \reals$, we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.%
        \footnote{\raf{This assumption is for technical convenience...}}
	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
\end{lemma}
\begin{proof}
  As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
  We proceed in two cases, depending on $|\Y|$. \jessiet{Seems really pedantic, but do we need to specify $\Y$ finite or $\Y = \reals$?  Since, for example, $\Y = \mathbb{Z}$ doesn't fit in either case, but isn't ruled out by our Lemma statement.}

@@

  \emph{$\Y=\reals$: }
  Any $L \in \Lcvx_d$ satisfies the assumptions of~\cite{ioffe1969minimization}, so we may interchange subdifferentiation and expectation.
  Specifically, letting $\V_{u,p} = \{V:\Y\to\reals^d \mid V \text{ measurable}, V(y) \in \partial L(u,y) \text{ $p$-a.s.}\}$, we have
  $\partial \E_p L(u,Y) = \{\int V(y)dp(y) \mid V\in\V_{u,p}\}$.
  As $\vec 0 \in \partial \E_p L(u,Y)$, in particular, there is some $V_{u,p} \in \V_{u,p}$ such that $\E_p V_{u,p} = 0$.
  \jessiet{Fleshing this out: $\exists E \subseteq \mathcal{B}(\Y)$ so that $p(E) = 0$ and $V(y) \in \partial L(u,y) \forall y \in E^c$.  Claim $q(E) = 0$, which would complete the claim that $V(y) \in \partial L(u,y) q$-a.s.  For contradiction, if $q(E) > 0$, then $\exists x \in E$ and open neighborhood $N_x \ni x$ with $q(N_x) > 0$.  Since $\supp(p) = \supp(q)$, we then have $p(N_x) >0$, contradicting $p(E) = 0$, and hence $V(y) \in \partial L(u,y)$ not $p$-a.s.  Therefore, we must have $q(E) = 0$, so $V(y) \in \partial L(u,y) q$-a.s.}
  For any $q\in\P$, as by assumption $q$ is supported on the same set as $p$, we have $V_{u,p}(y)\in\partial L(u,y)$ $q$-a.s., so that $V_{u,p}\in\V_{u,q}$\raft{I'm a bit too tired to see exactly how this follows, but it seems intuitively obvious. I'm okay to punt on it for the submission, but if someone has time to check, that would be great!}.
  Thus, $\E_q V_{u,p} = 0$ implies $0\in\partial\E_q L(u,Y)$ by the above.
  \raft{For posterity, the bug: we want to conclude $\E_q V_{u,p} = 0 \implies q \in \Gamma_u$.  But the ``a.s.\ in $p$'' means we may not have $0 \in \partial \E_q L(u,Y)$, since maybe $V_{u,p}(y)$ is not in $\partial L(u,y)$ a.s.\ in $q$...}
